---
title: "Introduction to R Participants"
output: 
    html_document:
        css: slides/style.css
        toc: true
        toc_depth: 2
        toc_float: true
        df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

```{r}
# Load packages

library(tidyverse)
library(googlesheets4)
library(janitor)
library(lubridate)
library(tigris)
library(hrbrthemes)
library(gendercodeR)
library(ggmap)
library(leaflet)
library(scales)
```

```{r}
# Set plotting default theme

theme_set(theme_ipsum(base_family = "Karla",
                      axis_title_family = "Karla",
                      axis_title_just = "m",
                      grid = "Yy"))
```



```{r}
# Import our data

survey_responses <- read_sheet("https://docs.google.com/spreadsheets/d/1w0cjfzCsBVMSDCycyAEtvyVUncSfG82odGH6l5VEawY/edit#gid=526375458") %>% 
  # Make the variable names easy to work with
  clean_names() 
```

# About our Respondents

```{r}
number_of_responses <- nrow(survey_responses)
```

We received responses from `r number_of_responses` people. 

## Locations

The map below shows the locations of respondents. 

```{r fig.height=6}
respondent_locations <- survey_responses %>% 
  drop_na(where_will_you_be_joining_the_e_study_from) %>% 
  mutate_geocode(where_will_you_be_joining_the_e_study_from) %>% 
  select(where_will_you_be_joining_the_e_study_from, lon, lat)

leaflet(respondent_locations) %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lon, ~lat,
                   color = "#FF7400",
                   stroke = FALSE, 
                   fillOpacity = 0.7,
                   popup = ~where_will_you_be_joining_the_e_study_from,
                   clusterOptions = markerClusterOptions(showCoverageOnHover = FALSE))
```



# R Expertise

```{r}
mean_expertise <- survey_responses %>% 
  summarize(mean_expertise = mean(how_would_you_rate_your_level_of_expertise_working_with_r, na.rm = TRUE)) %>% 
  mutate(mean_expertise = round_half_up(mean_expertise, 1)) %>% 
  pull(mean_expertise)
```

On a 10-point scale, respondents listed their level of expertise with R as `r number(mean_expertise, .1)`. The figure below shows the distribution of responses.

```{r fig.height = 4}
survey_responses %>% 
  drop_na(how_would_you_rate_your_level_of_expertise_working_with_r) %>% 
  count(how_would_you_rate_your_level_of_expertise_working_with_r) %>% 
  ggplot(aes(how_would_you_rate_your_level_of_expertise_working_with_r, n)) +
  geom_col(fill = "#6CABDD")+
  geom_text(aes(label = n),
            vjust = -1.5,
            color = "#6CABDD") +
  coord_cartesian(clip = "off") +
  scale_x_continuous(limits = c(0, 10),
                     breaks = seq(0, 10, by = 1),
                     labels = c("0\nNovice",
                                "1", "2", "3", "4", "5", "6", "7", "8", "9",
                                "10\nExpert")) +
  scale_y_continuous(labels = number_format(accuracy = 1)) +
  labs(title = str_wrap("How would you rate your level of expertise working with R?", 40),
       x = "Self-rated level of expertise",
       y = "Number of responses") +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title = element_text(hjust = 0.5,
                                  margin = margin(b = 20, unit = "pt"))) 
```


# Excitement/Nervousness

```{r}
mean_excitement <- survey_responses %>% 
  summarize(mean_excitement = mean(on_a_scale_from_terrified_to_excited_how_do_you_feel_about_the_process_of_learning_r, na.rm = TRUE)) %>% 
  mutate(mean_excitement = round_half_up(mean_excitement, 1)) %>% 
  pull(mean_excitement)
```

On a 10-point scale, respondents listed their level of excitement about learning R as `r number(mean_excitement, .1)`. The figure below shows the distribution of responses.

```{r fig.height = 4}
survey_responses %>% 
  drop_na(on_a_scale_from_terrified_to_excited_how_do_you_feel_about_the_process_of_learning_r) %>% 
  count(on_a_scale_from_terrified_to_excited_how_do_you_feel_about_the_process_of_learning_r) %>% 
  ggplot(aes(on_a_scale_from_terrified_to_excited_how_do_you_feel_about_the_process_of_learning_r, n)) +
  geom_col(fill = "#6CABDD")+
  geom_text(aes(label = n),
            vjust = -1.5,
            color = "#6CABDD") +
  coord_cartesian(clip = "off") +
  scale_x_continuous(limits = c(0, 10),
                     breaks = seq(0, 10, by = 1),
                     labels = c("0\nTerrified",
                                "1", "2", "3", "4", "5", "6", "7", "8", "9",
                                "10\nExcited")) +
  scale_y_continuous(labels = number_format(accuracy = 1)) +
  labs(title = "How excited are you to learn R?",
       x = "Excitement level",
       y = "Number of responses") +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title = element_text(hjust = 0.5,
                                  margin = margin(b = 20, unit = "pt"))) 
```

# Tools People Currently Use


```{r}
other_tools <- survey_responses %>% 
  select(contains("what_software")) %>% 
  pivot_longer(cols = everything(),
               names_to = "type_of_work",
               values_to = "tool") %>% 
  mutate(type_of_work = case_when(
    str_detect(type_of_work, "analysis") ~ "Data Analysis",
    str_detect(type_of_work, "visualization") ~ "Data Visulization"
  )) %>% 
  separate_rows(tool, sep = ", ") %>% 
  mutate(tool = fct_other(tool,
                          keep = c("Excel", "R", "SAS", "SPSS", "Stata", "Tableau", "Powerpoint"),
                          other_level = "Other")) %>% 
  count(type_of_work, tool)
```

```{r fig.height = 8}
ggplot(data = other_tools,
       aes(x = tool,
           y = n,
           label = n)) +
  geom_col(fill = "#6CABDD") +
  geom_text(aes(label = n),
            vjust = -1.5,
            color = "#6CABDD") +
  coord_cartesian(clip = "off") +
  facet_wrap(~type_of_work,
             ncol = 1,
             scale = "free_x") +
  labs(x = NULL,
       y = NULL) +
  theme(strip.text.x = element_text(face = "bold",
                                    margin = margin(b = 20, unit = "pt")))
```

